### 2020-01-21 manuscript/bef_stability/manuscript.Rmd
Add dataset description: *_network_* and *_community_*

```{r}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

@@

```{r get-data}
library(nlme)
library(piecewiseSEM)

@@

```{r mod-div-troph}
stab_troph_mod <- lme(data = na.omit(stab_div_troph),
  fixed = log_stab ~ log_rich + troph_group + log_rich:troph_group,
  random = ~ 1 | basin,
  control = ctrl
)

@@

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
filter(stab_div_troph, log_rich < 0)
# Plot left  
p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

>>>>

```{r, echo = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

@@

```{r get-data, cache = TRUE}
library(nlme)
library(piecewiseSEM)

@@

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lme(data = na.omit(stab_div_troph),
  fixed = log_stab ~ log_rich + troph_group + log_rich:troph_group,
  random = ~ 1 | basin,
  control = ctrl
)

@@

```{r p-s-div}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
# Plot left  
p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich) +
  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

### 2020-01-21 report/02-methods.Rmd
Add dataset description: *_network_* and *_community_*

@@

```{r}
match_st <- match(hab_type$station, com_mat$station)
hab_type <- hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
u_hab  <- unique(hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

@@

```{r}
ts_biomass <- community_metrics %>%
  select(station, date, biomass) %>%
  mutate(station = as.character(station)) %>%
  group_by(station) %>%
  arrange(date) %>%
  nest()

>>>>

## Describe datasets

### Community and network datas

- \*\_analysis (data in general by species and fishing operation):
  - community_analysis:
    - by species and by fishing operation:
      - number of individuals
      - mean length   
      - sum of biomass
  - network_analysis:
    - by fishing operation:
      - data:
	-length, class and species of each individual
      - network:
	- feeding link between species in the igraph::graph_from_data_frame()
	  format
	- from to: the "from" is eaten by "to", i.e. the biomass goes "from" "to"
      - composition (by opcod and by species):
	- troph_level: trophic level of the species
	- biomass: species biomass
	- troph_group: high (group 3) or low predator (group 2)

- \*\_metrics (metrics by fishing operation):
  - community_metrics:
    - richness: species richness
    - nind: number of individuals
    - biomass: sum of biomass
    - sp_vector: named vector of species biomass (name corresponding to species)
    - rel_bm: named vector of relative species biomass (name corresponding to species)
    - pielou: pielou index on biomass distribution of species
    - simpson: simpson index on biomass distribution of species
  - network_metrics:
    - from data to troph_group: see network_analysis
    - nestedness: network index
    - modul_guimera: guimera modularity index
    - diet_overlap: matrix of diet overlap between species pair 
    - avg_diet_overlap: mean diet overlap between species pair
    - connectance: network index 
    - nbnode: nb of nodes in the network (i.e. species or species classes plus
      resources as detrivor, zooplankton, phytoplankton)
    - compartiment: compartimentation index of the network 
    - troph_level_avg: mean trophic level of the network  
    - troph_length: trophic length of the network
    - modularity: modeularity of the network
    - connectance_corrected: residuals of the relationship between connectance
      and nbnode
    - modularity_corrected: cf above
    - troph_level_avg_corrected: cf above 
    - mean_troph_level_corrected: cf above
    - w_trph_lvl_avg: mean trophic level of the network WEIGHTED by biomass

- temporal\_\*\_metrics (metrics summarised by station):
  - temporal_community_metrics (cf community_metrics for the index):
    - \*\_avg: mean of the index  
    - \*\_cv: cv of the index
    - \*\_med: median of the index 
    - \*\_stab: stab of the index (i.e. 1/cv)
    - betadiv\_\*: $\beta$-diversity 
      - betadiv: mean dissimilarity between year for species composition
      - \*\_bin: binary species composition (0 or 1)
      - \*\_diag: dissimilarity between year to year (diagonal of the
	dissimilarity matrix)
  - temporal_network_metrics (cf network_metrics for the index):
    - same principle than for temporal_community_metrics
    - troph_group

### Station data

- op_analysis:
  - protocol_type: type of fishing (complete or partial)
  - opcod: id of the fishing operation
  - date: date (YYYY-MM-DD) of the fishing operation
  - station: id of the station
  - protocol: protocole name (complete, partial_by_point, partial_over_bank)
  - surface: surface sampled
  - nb_sp: number of the species sampled for the fishing operation
  - nb_ind: number of the individuals sampled for the fishing operation
  - year: year at which the fishing operation was done  
  - length_sourced: length of river fished

@@

```{r, eval = FALSE}
match_st <- match(hab_type$station, com_mat$station)
hab_type <- hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
u_hab  <- unique(hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

@@

```{r}
ts_biomass <- community_metrics %>%
  dplyr::select(station, date, biomass) %>%
  mutate(station = as.character(station)) %>%
  group_by(station) %>%
  arrange(date) %>%
  nest()
